%----------------------------------------------------------------------------------------
%	TALKS SECTION
%----------------------------------------------------------------------------------------

\section{Outreach} % \small(\,=\,~invited)

\begin{multicols}{2}

\subsection{Invited talks and workshops}

%% 2025
\mycvitem{2025}{\textbf{Moss, F. C.} \emph{Round-table discussion}. Le Studium conference, ``The Digital Edition of Medieval to Early Modern Song `Song': Methodological and Interpretative Perspectives''. 13--15 May 2025, Centre d'Études Supérieures de la Renaissance (CESR), Tours, France.}
\mycvitem{}{\textbf{Moss, F. C.} \& Lesemann-Elliott, C. \emph{Data collecting from musical sources}. EarlyMuse COST Action 21161, Working Group 2 ('Sources'). 
  Institute of Musicology of the Slovak Academy of Sciences \& University Library, 17--19 March, 2025, Bratislava, Slovakia.}

%% 2024
\mycvitem{2024}{\textbf{Moss, F. C.} \emph{Computational Musicology: oxymoron or perfect fit?} Graduate Schools Day, Julius-Maximilians-Universität Würzburg, 4 July 2024, Würzburg, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Künstliche Intelligenz und Musikwissenschaft}. Austrian Centre for Digital Humanities and Cultural Heritage (ACDH-CH) of the Austrian Academy of Sciences (ÖAW), Vienna, Austria, 17 Juni 2024.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Corpus Research and Choro: Potential and Challenges for Digital Methods}. 3 April 2024. School of Music, Universidade Federal do Rio de Janeiro, Rio de Janeiro, Brazil.}

%% 2023
\mycvitem{2023}{\textbf{Moss, F. C.} \emph{Virtual Tonal Spaces (VTS): towards an interactive digital environment for music theory}. Tag der Lehre 2023. Julius-Maximilians-Universität Würzburg, 22 November 2023, Würzburg, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{10 secret rules for a degree in DH -- you won't believe no. 7!!}. 1st DH Alumni Event, 17 November 2023. Digital Humanities Insitute, École Polytechnique Fédérale de Lausanne, Switzerland.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Counting notes: Research questions and methods in music corpus studies}. Seminar ``History and Theory of Digital Humanities'', Université de Lausanne, Lausanne, Switzerland, 12 October 2023.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Töne zählen: Forschungsfragen und Methoden musikwissenschaftlicher Korpusstudien in historischer und epistemologischer Perspektive}. Talk in lecture series ``Transdisziplinäre Aspekte digitaler Methodik in den Geistes- und Kulturwissenschaften'', Leibniz-Institut für Europäische Geschichte, Mainz, Germany, 28 June, 2023.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Musik Er-Zählen: Einblicke in die digitale Korpusforschung.} Vortrag im Institutskolloquium des Instituts für Musikforschung, JMU, 20 June, 2023.}{}
\mycvitem{}{\textbf{Moss, F. C.} Respondent to Sanja Kiš Žuvela: \emph{Musical Terminology, Digital Corpus Management and Translation}. GMTH International Music Theory Lectures. 9 February, 2023.}
\mycvitem{}{Arthur, C., Baker, D., Burgoyne, J. A., Cecchetti, G., Eerola, T., Farbood, M., Finkensiep, C., Harrison, P., Koelsch, S., Margulis, E., \textbf{Moss, F. C.}, Neuwirth, M., Pearce, M., Pelofi, C., Rammos, Y., Rohrmeier, M., \& Volk, A. \emph{Decoding Musical Structure: Theory, Computation, and Neuroscience} (Workshop). Congressi Stefano Franscini, Monte Verità, 5--9 February, 2023.}

%% 2022
\mycvitem{2022}{ \textbf{Moss, F. C.} \emph{Music Stylometry -- the Case of Choro}. Music Cognition Lab Meeting, Princeton University [online], 2 November, 2022.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Learning about Machine Learning with CRIM}. Digital Counterpoints: Exploring Similarity in Renaissance Music, October 20--22, 2022, Haverford College, Department of Music, Haverford, PA.}
\mycvitem{}{ \textbf{Moss, F. C.} \emph{midiVERTO: A web-based tool to make computational music analysis more accessible}. Institute für Musik und Musikwissenschaft, Technische Universität Dortmund, Germany, 28 April.}
\mycvitem{}{ \textbf{Moss, F. C.} \emph{Interactive Music Analysis using the DFT and Pitch-Class Distributions extracted from MIDI files}. Faculdade de Engenharia da Universidade do Porto (FEUP), Porto, Portugal, 4 April 2022.}
\mycvitem{}{ \textbf{Moss, F. C.} \emph{Music Theory and the Discrete Fourier Transform}. Cognitive and Systematic Musicology Lab Meeting, The Ohio State University, Columbus, USA [online], 25 March 2022.}

%% 2021
\mycvitem{2021}{ \textbf{Moss, F. C.} \emph{The Science of Music.} EPFL Information Days, 24--25 November 2021, Lausanne, Switzerland. \url{https://youtu.be/y5TQN09zDVI}}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Boosting Open Research in Empirical Musicology}. EPFL Data Champions Meeting (DCBreak\#3). March 18, 2021, Lausanne, Switzerland [online].}

%% 2020
\mycvitem{2020}{\textbf{Moss, F. C.} \emph{The Importance of Modeling in Computational Musicology}. Round-table on ``Probability and Music'', 5th International Congress of Music and Mathematics (MusMat 2020) -- Perspectives and Applications of Mathematics in Post-Tonal Theories («Homage to Jamary Oliveira»),
    December 8--12, Rio de Janeiro, Brazil [online].}
    \mycvitem{}{\textbf{Moss, F. C.} \emph{Data-Driven Music History}. Workshop for the International Conference of Students of Systematic Musicology, York University, September 14, 2020, York, UK [online].}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Computational Musicology and the Digital Humanities: Problems, Practices, and Prospects}. CRETA-Werkstatt \#9, Center for Reflected Text Analytics, University of Stuttgart, February 18, 2020, Stuttgart, Germany.}

%% 2019
\mycvitem{2019}{\textbf{Moss, F. C.} \emph{Tracing the History of Tonality with Note Distributions}. ``Corpus Research as a Means of Unlocking Musical Grammar'' International Research Workshop, July 1--4, 2019, Tel-Aviv, Israel.}

%% 2018
\mycvitem{2018}{\textbf{Moss, F. C.} \emph{Corpus Research in Digital Musicology}. Seminar ``Willkommen in der Matrix: Digitale Anwendungen f{\"u}r die Musikanalyse in Theorie und Praxis'', University of Basel, Basel, Switzerland.}

%% 2017
\mycvitem{2017}{\textbf{Moss, F. C.} \emph{Formal Grammars and Ambiguity in Extended Tonality}. Workshop and Symposium on Schenkerian Analysis ``Wege der Kreativit{\"a}t -- Zwischen Erfindung und Rekonstruktion'', Universit{\"a}t der K{\"u}nste, Berlin, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{From Beethoven to Brazil: Digital Musicology at EPFL}. Digital Synergies: Ca' Foscari meets École Polytechnique Fédérale de Lausanne. Global Challenges Seminar - Team ``Creative arts, cultural heritage and digital humanities'', Venice, Italy.}

%% 2016
\mycvitem{2016}{\textbf{Moss, F. C.} \emph{Extended Tonality: Theoretical Challenges and their Relation to the Neuroscientific Study of Musical Syntax}. Max Planck Institute for Human Cognitive and Brain Sciences, Leipzig, Germany. }
\mycvitem{}{\textbf{Moss, F. C.}, Rohrmeier, M. \emph{Towards a syntactic account for harmonic sequences in extended tonality}. Syntax Square Meeting, Massachusetts Institute of Technology, Department of Linguistics and Philosophy, Cambridge, USA.}
\mycvitem{}{\textbf{Moss, F. C.} \& Harasim, D. \emph{Extended Tonality and Music Cognition}. Symposium ``Towards a World Music Theory'', University of Hamburg, Institute for Systematic Musicology, Hamburg, Germany.}

\subsection{Conference presentations}

%% 2025 
%\mycvitem{2025}{Roeder, T., Klinger, J., Stickler, F., Keupp, C., \& \textbf{Moss, F. C.} \emph{Multimodality and Minimal Publishing: TEI, MEI and more in 19th-Century Music Treatises}. 25th Annual Meeting of the Text Encoding Initiative. 16--17 September 2025, Kraków, Poland.}
\mycvitem{2025}{\textbf{Moss, F. C.} \emph{Vuza-Kanons: ein mathematisches Konzept zur Beschreibung nicht-überlappender Rhythmen}. XXIV. Kontrapunktwerkstatt. 8--10 May, 2025, Basel, Switzerland.}
\mycvitem{}{Nachtwey, A., \& \textbf{Moss, F. C.} \emph{Beyond Bars: Distribution of Differences in Music Prints}. Music Encoding Conference 2025. 3--6 June 2025, London, UK.}
\mycvitem{}{Stickler, F., Roeder, T., \& \textbf{Moss, F. C.} \emph{A Minimal Publishing Model for Text and Music Notation}. Music Encoding Conference 2025. 3--6 June 2025, London, UK.}

%% 2024
\mycvitem{2024}{\textbf{Moss, F. C.} \& Nakamura, E. \emph{Modeling the evolution of harmony in popular music from different cultural contexts}. CHR2024: Fifth Conference on Computational Humanities Research, 4--6 December 2024, Aarhus, Denmark.}
\mycvitem{}{Hofmann, L., Sapp, C. S., \& \textbf{Moss, F. C.} \emph{Metrical Irregularities and Polymetric Structures in Hugo Distler's Vocal Works: Towards a Digital Corpus Study.} 2nd International Conference on Computational and Cognitive Musicology, 17--18 October 2024, Utrecht, The Netherlands.}
\mycvitem{}{Nachtwey, A. \& \textbf{Moss, F. C.} \emph{Digitale Korpusbildung in der Musikforschung: Herausforderungen und Lösungsansätze für die quantitative Analyse von Musikeditionsvarianten.} Jahrestagung der Gesellschaft für Musikforschung 2024, 11--14 September 2024, Cologne, Germany.}
\mycvitem{}{Hofmann, L. \& \textbf{Moss, F. C.} \emph{``Zeitgemäß polyphon''. Zur Kodierung und Modellierung von Polymetrik und metrischer Irregularität in Hugo Distlers Vokalwerken.} Jahrestagung der Gesellschaft für Musikforschung, 11--14 September 2024, Cologne, Germany.}
\mycvitem{}{Eipert, T. \& \textbf{Moss, F. C.} \emph{Digital Paths Through History: Phylogenetic Analysis of Medieval Chants from the Graduale Synopticum Data.} [Poster] Jahrestagung der Gesellschaft für Musikforschung, 11--14 September 2024, Cologne, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \& Nakamura, E. \emph{Cross-cultural modeling of the evolution of harmony in popular music}. Cultural Evolution Society Conference (CES 24), 9--11 September 2024, Durham, UK.}
\mycvitem{}{Eipert, T., \textbf{Moss, F. C.}, \& Vlhóva-Wörner, H. \emph{Reconstructing the Formation of Trope Traditions through Network Models}. Annual International Medieval and Renaissance Music Conference (MedRen) 2024, 6--9 July, 2024, Granada, Spain.}
\mycvitem{}{Polykarpidis, P., Kalofonos, Dionysios., \textbf{Moss, F. C.}, \& Anagnostopoulou, C. \emph{Echos (mode) classification in heirmologic corpora of Byzantine music}. [Poster] Annual International Medieval and Renaissance Music Conference (MedRen) 2024, 6--9 July, 2024, Granada, Spain.}
\mycvitem{}{Hofmann, T., Sapp, C., \& \textbf{Moss, F. C.} \emph{Encoding polymeters and metric irregularities in selected motets from Hugo Distler's \emph{Der Jahrkreis} op. 5 using different music encoding formats.} ECHOES conference ``Digital Technologies Applied to Music Research: Methodologies, Projects and Challenges'', 27-29 June 2024, Lisbon, Portugal.}
\mycvitem{}{Eipert, T., Hartelt, A., \textbf{Moss, F. C.}, Puppe, F. \emph{Medieval Chant Lineages Unlocked: Leveraging Optical Music Recognition for Phylogenetic Analysis of Gregorian Proper.} ECHOES conference ``Digital Technologies Applied to Music Research: Methodologies, Projects and Challenges'', 27-29 June 2024, Lisbon, Portugal.}
\mycvitem{}{Pereira, S., Affatato, G., Bernardes, G., \& \textbf{Moss, F. C.} \emph{Fourier Qualia Wavescapes: Hierarchical Analyses of Set Class Quality and Ambiguity}. 9th International Conference on Mathematics and Computation in Music (MCM2024). Universidade de Coimbra, Coimbra, Portugal, 18--21 June 2024.}

% 2023
\mycvitem{2023}{Nakamura, E., Eipert, T. \& \textbf{Moss, F. C.} \emph{Historical Changes of Modes and their Substructure Modeled as Pitch Distributions in Plainchant from the 1100s to the 1500s}. 16th International Symposium on Computer Music Multidisciplinary Resarch (CMMR2023), 13--17 November 2023, Tokyo, Japan.}
\mycvitem{}{Eipert, T. \& \textbf{Moss, F. C.} \emph{MonodiKit: A data model and toolkit for the Corpus Monodicum}. The 10th International Conference on Digital Libraries for Musicology (DLfM '23), 10 November 2022, Milano, Italy.}{}
\mycvitem{}{Eipert, T. \& \textbf{Moss, F. C.} \emph{Communities in Medieval Troper Networks are Shaped by Carolingian Politics}. Poster. The 10th International Conference on Digital Libraries for Musicology (DLfM '23), 10 November 2022, Milano, Italy.}{}
\mycvitem{}{Yust, J., Affatato, G., \& \textbf{Moss, F. C.}. \emph{Animated Harmonic Analysis Using DFT Phase Spaces and Coefficient Products}. Joint Annual Meeting of the American Musicological Society (AMS) and the Society for Music Theory (SMT), 9--12 November 2023, Denver, Colorado.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Korpusforschung und Digitale Edition: ein Plädoyer für stärkere Intradisziplinarität}. Beitrag im Panel ``Musikalische Korpusforschung: Aktuelle Trends und Herausforderungen'', mit Markus Neuwirth, Martin Rohrmeier, Christof Weiß, Johannes Hentschel \& Maik Köster. Jahrestagung der Gesellschaft für Musikforschung, 4--7 October, 2023, Saarbrücken, Germany.}
\mycvitem{}{Eipert, T., Frieler, K., \& \textbf{Moss, F. C.} \emph{Inside or Outside: The Use of Scales in Jazz Solo Improvisations}. Poster.Jahrestagung der Gesellschaft für Musikforschung, 4--7 October, 2023, Saarbrücken, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} [Cancelled.] \emph{Star Plots: eine neue Methode zur Visualisierung harmonischer Pfade für vierstimmige Kompositionen}. 23. Jahreskongress der Gesellschaft für Musiktheorie (GMTH) ``Musiktheorie und Künstlerische Forschung'', 22-24 September 2023, Hochschule für Musik Freiburg, Freiburg im Breisgau, Germany.}
\mycvitem{}{Roeder, T., Köster, M., \& \textbf{Moss, F. C.} \emph{Music-Text Interlinking as a Challenge for Digital Encodings of Music-Theoretical Writings}. Encoding Cultures -- Joint MEC and TEI Conference 2023, 4--8 September 2023, Zentrum Musik -- Edition -- Medien (ZenMEM), Paderborn, Germany.}
\mycvitem{}{Eipert, T. \& \textbf{Moss, F. C.} \emph{A system of trope elements: using network models to understand interrelations within the transmission of trope complexes}. Annual International Medieval and Renaissance Music Conference (MedRen) 2023, 24--28 July, 2023, Munich, Germany.}

% 2022
\mycvitem{2022}{\textbf{Moss, F. C.}, Nápoles López, N., Köster, M. \&  Rizo, D. \emph{Challenging sources: a new dataset for OMR of diverse 19th-century music theory examples}. 4th International Workshop on Reading Music Systems (WoRMS 2022), 18 November 2022 [online].}
\mycvitem{}{Köster, M. \& \textbf{Moss, F. C.} \emph{Der harmonische Dualismus und seine Entwicklung zum `Streit- und Angelpunkt der Musiktheorie' -- eine Diskursanalyse}. Jahrestagung der Gesellschaft für Musikforschung. Nach der Norm: Musikwissenschaft im 21. Jahrhundert, 29 September -- 1 October 2022, Humboldt-Universität Berlin, Berlin, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \& Métrailler, C. [Cancelled.] \emph{Reading Music Theory from a Distance: A Corpus Study of the Thesaurus Musicarum Italicarum}. 21st Quinquennial Congress of the International Musicological Society (IMS2022), 22--26 August 2022, Athens, Greece.}
\mycvitem{}{\textbf{Moss, F. C.}, Affatato, G. \& Harasim, D. \emph{Phantom Curves: Scientific Discovery through Interactive Music Visualization}. The 9th International Conference on Digital Libraries for Musicology (DLfM), In association with the annual conference of the International Association of Music Libraries (IAML), 28 July 2022, Prague, Czech Republic.}{}
\mycvitem{}{Harasim, D., Affatato, G., \& \textbf{Moss, F. C.}. \emph{midiVERTO: A Web Application to Visualize Tonality in Real Time}. 8th International Conference on Mathematics and Computation in Music (MCM2022). Georgia State University, Atlanta, USA, 21--24 June 2022.}
\mycvitem{}{Bracks, C. \& \textbf{Moss, F. C.} \emph{Totoli's Art of Lelegesan: Analyzing Sociocultural Context and Musical Content.} 10th International Workshop on Folk Music Analysis 2022 (FMA2022), University of Sheffield, Sheffield, UK, June 14--17, 2022.}
\mycvitem{}{Meng, S., \textbf{Moss, F. C.}, \& Rohrmeier, M. \emph{Revisiting Tong Yun San Gong theory in Chinese music: a corpus study of Chinese folksongs.} 7th Analytical Approaches to World Music Conference (AAWM2022), University of Sheffield, Sheffield, UK, June 14--17, 2022.}

% 2021
\mycvitem{2021}{\textbf{Moss, F. C.}, Köster, M., Femminis, M., Métrailler, C., \& Bavaud, F. \emph{Digitizing a 19th-century music theory debate for computational analysis}. CHR 2021: Computational Humanities Research Conference,
November 17--19, 2021, Amsterdam, The Netherlands [online].}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Polytonality and the Emergence of Tone Fields in Tailleferre's \emph{Pastorale}}. 21. Jahreskongress der Gesellschaft für Musiktheorie (GMTH) -- Tonsysteme und Stimmungen.
    October 1--3, 2021, Musik-Akademie Basel/Hochschule für Musik (FHNW), Basel, Switzerland.}
\mycvitem{}{Hentschel, J., \textbf{Moss, F. C.}, Markus Neuwirth, \& Rohrmeier, M. \emph{Die Entwicklung der tonalen Sprache in Beethovens Streichquartetten: Eine vergleichende Korpusstudie der Schaffensphasen}. XVII. Internationaler Kongress der Gesellschaft für Musikforschung, Universität Bonn, Abteilung für Musikwissenschaft/Sound Studies und Beethoven-Archiv des Beethoven-Hauses Bonn
Bonn, Germany, September 28 -- October 1 2021, Bonn, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Digitizing the Dualism Debate: a case study in the computational analysis of historical music theory sources}. CROSS 2021 Event. 16 September 2021, École Polytechnique Fédérale de Lausanne/Université de Lausanne, Lausanne, Switzerland.}
\mycvitem{}{\textbf{Moss, F. C.}, Herff, S. A., \& Rohrmeier, M. \emph{Modeling perceived tonal stability of individual and aggregated listener responses for scales and cadences}. 16th International Conference on Music Perception and Cognition \& 11th triennial conference of the European Society for the Cognitive Sciences of Music. July 28--31, Sheffield, UK [online].}
\mycvitem{}{\textbf{Moss, F. C.}, Herff, S. A., \& Rohrmeier, M. \emph{Individual perception of diatonic scales predicts perceived tonal fit in octatonic and hexatonic contexts}. 16th International Conference on Music Perception and Cognition \& 11th triennial conference of the European Society for the Cognitive Sciences of Music. July 28--31, Sheffield, UK [online].}
\mycvitem{}{Hentschel, J., \textbf{Moss, F. C.}, McLeod, A., \& Rohrmeier, M. \emph{Towards a Unified Model of Chords in Western Harmony}. Music Encoding Conference [online].}
\mycvitem{}{Anzuoni, E., Ayhan, S., Dutto, F., McLeod, A., \textbf{Moss, F. C.}, \& Rohrmeier, M. \emph{A Historical Analysis of Harmonic Progressions Using Chord Embeddings}. 18th Sound and Music Computing Conference [online].}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Discovering the line of fifths in a large historical corpus}. Future Directions of Music Cognition, The Ohio State University, March 6--7, 2021, Columbus, OH [online]. \url{https://doi.org/10.17605/OSF.IO/J5W6T}}

%% 2020
\mycvitem{2020}{\textbf{Moss, F. C.} \emph{Analyzing musical pieces on the Tonnetz using the \emph{pitchplots} Python library}. 20. Jahreskongress der Gesellschaft für Musiktheorie
    (GMTH), Hochschule für Musik Detmold, October 1--4, 2020, Detmold, Germany [online].}
% 2019
\mycvitem{2019}{\textbf{Moss, F. C.} \emph{Transitions of Tonality: Perspectives on the Historical Changes of Tonal Pitch Relations from Computational Musicology, Music Theory, and the Digital Humanities}. University of Cologne, November 29, 2019, Cologne, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Inferring Tonality from Note Distributions -- Why Models Matter (Poster)}. SEMPRE Graduate Conference 2019, Cambridge, UK.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Analyzing Tonality with Note Distributions}. First Swiss Digital Humanities Student Exchange DHX2019, Basel, Switzerland. }

% 2018
\mycvitem{2018}{\textbf{Moss, F. C.}, Souza, W. F. \& Rohrmeier, M. \emph{Harmony and Form in Brazilian Choro: A Corpus Study}. 15th International Conference on Music Perception and Cognition \& 10th triennial conference of the European Society for the Cognitive Sciences of Music, Graz, Austria. }
\mycvitem{}{Aitken, C., O'Donnell, T. \& Rohrmeier, M. [Poster presented by \textbf{Moss, F. C.}]. \emph{A Maximum Likelihood Model for the Harmonic Analysis of Symbolic Music}. 15th Sound and Music Computing Conference ``Sonic Crossings''. Limassol, Cyprus.}
\mycvitem{}{Harasim, D., \textbf{Moss, F. C.} \& Ramirez, M. \emph{A Brief History of Tonality} (Poster). Applied Machine Learning Days, EPFL, Switzerland.}

% 2017
\mycvitem{2017}{\textbf{Moss, F. C.}, Souza, W. F. \& Rohrmeier, M. \emph{Brazilian Choro: A New Data Set of Chord Transcriptions and Analyses of Harmonic and Formal Features}. 17. Jahreskongress der Gesellschaft f{\"u}r Musiktheorie (GMTH) \& 27. Arbeitstagung der Gesellschaft f{\"u}r Popularmusikforschung (GfPM) ``Popul{\"a}re Musik und ihre Theorien: Begegnungen -- Perspektivwechsel -- Transfers'', Graz, Austria. }
\mycvitem{}{\textbf{Moss, F. C.}, Harasim, D., Neuwirth, M. \& Rohrmeier, M. \emph{Beethovens Streichquartette -- ein XML-basierter Korpus harmonischer Analysen in einem neuen Annotationssystem}. Jahrestagung der Gesellschaft f{\"u}r Musikforschung, Kassel, Germany.}
\mycvitem{}{\textbf{Moss, F. C.}, Rohrmeier, M. \emph{Integrating Transformational and Hierarchical Models of Extended Tonality}. 9th European Music Analysis Conference (EuroMAC), Strasbourg, France.}
\mycvitem{}{Rom, U., Je\ss ulat, A., \textbf{Moss, F. C.} \& Guter, I. \emph{Ambiguity, Illusion \& Timelessness in Late and Post-Tonal Harmony}. Panel discussion at the 9th European Music Analysis Conference (EuroMAC), Strasbourg, France.}
\mycvitem{}{\textbf{Moss, F. C.}, Rohrmeier, M. \& Bravo, F. \emph{Emotional Associations Evoked by Structural Properties of Musical Scales and Abstract Visual Shapes}. KOSMOS Dialogue ``Music, Emotion, and Visual Imagery'', Berlin, Germany.}
\mycvitem{}{Harasim, D., \textbf{Moss, F. C.}, Neuwirth, M. \& Rohrmeier M. \emph{Beethoven's String Quartets: Introducing an XML-Based Corpus of Harmonic Labels Using a New Annotation System}. Music Encoding Conference, Tours, France.}

% 2016
\mycvitem{2016}{\textbf{Moss, F. C.}, Rohrmeier, M. \emph{Structural Ambiguities in Language and Music} (Poster). Helsinki Summer School for Cognitive Neuroscience 2016 (HSSCN 2016).}
\mycvitem{}{\textbf{Moss, F. C.}, Rohrmeier, M.  \emph{A grammatical approach to tension-resolution patterns in extended tonal harmony}. Meeting of the Computational Cognitive Science Group, Massachusetts Institute of Technology, Department of Brain and Cognitive Sciences, Cambridge, USA.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Syntax of Extended Tonality: Towards a Grammar of Generalized Harmonic Functions}. Music Theory Colloquium, Boston University, College of Fine Arts, School of Music, Boston, USA.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Generalizing Harmonic Functions: A Grammatical Approach to Extended Tonality}. Yale University, Department of Music, New Haven, USA.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{Music Cognition and Extended Tonality: Theoretical Challenges and Empirical Implications}. Research Colloquium, University of Cologne, Cologne, Germany.}

% 2015
\mycvitem{2015}{\textbf{Moss, F. C.} \emph{On generative modelling of musical form}. Seminar ``Mathematics and Music'', TUD, Dresden, Germany.}
\mycvitem{}{\textbf{Moss, F. C.} \emph{`The terror of sanctity.' Tonal cues for resolving dramatic ambiguities in Wagner's Parsifal}. Seminar ``Understanding Musical Structures'', TUD, Dresden Germany.}

% 2014

\mycvitem{2014}{\textbf{Moss, F. C.} \emph{Tonality and functional equivalence: A multi-level model for the cognition of triadic progressions in 19th century music}. International conference of Students of Systematic Musicology, Goldsmiths University, London, UK.}
% \mycvitem{}{\textbf{Moss, F. C.} \emph{Language, music and the brain: a resource-sharing framework (Patel, 2012)}. Seminar ``Cognitive Neuroscience of Music'', Institut for Musicology, University of Cologne, Cologne, Germany.}

\subsection{Science Communication}
\mycvitem{2024}{\textbf{Moss, F. C.}, \emph{Musik und Mathematik -- Wie passt das eigentlich zusammen?}, Science Slam 2024, Julius-Maximilians-Universität Würzburg, 8 November 2024. \url{https://www.uni-wuerzburg.de/alumni/alle-veranstaltungen/science-slam/science-slam-2024/}}
\mycvitem{2021}{ Rohrmeier, M. \& \textbf{Moss, F. C.} \emph{Music, Mathematics, and the Geometry of Jazz}. Montreux Jazz Festival, July 11, 2021, Montreux, Switzerland. \url{https://www.montreuxjazzfestival.com/de/artist/martin-rohrmeier/}}
\mycvitem{2017}{\textbf{Moss, F. C.} \emph{Musik und Sprache}. Talk for Student Association ``Denkzettel'', TUD, Dresden, Germany.}

\end{multicols}
