\section{Teaching and mentoring}
\subsection{University courses}
\begin{multicols}{2}
    \mycvitem{Fall 2022}{``Neo-Riemannian Theories: Analysemethoden für erweiterte Tonalität von der Spätromantik bis zur Filmmusik'', seminar at JMU.}
    \mycvitem{}{``Music Memes: Quantitative Zugänge und Theorien zu kultureller Transmission von Musik'', seminar at JMU.}
    \mycvitem{Spring 2021}{``Musical Diversity across Historical Time'', lecture in class ``Digital Musicology'', EPFL.}
    \mycvitem{Fall 2020}{``Introduction to Musical Corpus Studies'', UzK.}
    \mycvitem{}{``Tonality: Perspectices of historical musicology and corpus studies'', lecture in ``Ringvorlesung Musikwissenschaft'', UzK.}
    \mycvitem{Spring 2020}{``Musical improvisation, invention and creativity'', teaching assistant, EPFL.}
    \mycvitem{}{``Musical Diversity across Historical Time'', lecture in class ``Digital Musicology'', EPFL.}
    \mycvitem{Spring 2018}{``Digital Musicology'', teaching assistant, EPFL.}
    \mycvitem{2016--2017}{``Reading Class Musicology'', with Christoph Wald, TUD.}
    \mycvitem{2015--2016}{``Introduction to Musicology'', with Christoph Wald, TUD.}
    \mycvitem{Spring 2013}{``Academic Writing and Research Techniques'', HfMT.}
\end{multicols}

\subsection{PhD thesis supervision}
\cvitem{2022--today}{Co-supervision of Shuxin Meng, Digital Humanities, École Polytechnique Fédérale de Lausanne (EPFL)}
\cvitem{Spring 2017}{Peer-mentoring visiting PhD student Willian Fernandes de Souza, Music Theory/Composition,
    Universidade Federal do Rio de Janeiro (UFRJ)}

\subsection{Master thesis supervision}
\cvitem{Spring 2020}{Co-supervision of Cédric Viaccoz, Digital Humanities, EPFL}

\subsection{Bachelor thesis supervsion}
\cvitem{Spring 2022}{Co-supervision of Iris Folpmers, Artificial Intelligence, UvA, \url{https://scripties.uba.uva.nl/search?id=record_29490}}

\subsection{Other mentoring}
\cvitem{Fall 2020}{3 Machine Learning graduate student projects on vector embeddings of harmony (EPFL)}
\cvitem{Fall 2019}{Machine Learning graduate student project on vector embeddings of harmony (EPFL)}
\cvitem{Fall 2018}{3 Machine Learning graduate student projects on chord prediction with neural networks (EPFL)}
\cvitem{Spring 2018}{4 Digital Musicology graduate student projects (EPFL)}
\cvitem{Fall 2015}{interdisciplinary project of technical design undergraduate, Technische Universität Dresden (TUD)}